---
title: "Overview of {DMC21cent} R Package"
output: 
  rmarkdown::html_document:
    df_print: paged
    theme: cerulean
    highlight: haddock
    toc: yes
    toc_depth: 2
    toc_float:
      collapsed: false
      smooth_scroll: true
    code_fold: show
---

```{r, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  echo = TRUE,
  eval = TRUE,
  warning = FALSE,
  message = FALSE,
  fig.width=10,
  fig.height=5,
 # dpi = 85,
  # out.width = "100%",
  # out.height = "50%",
  comment = "#>"
)
library(dplyr)
library(ggplot2)
library(scales)
library(plotly)
devtools::load_all()
```

```{r setup, eval = FALSE}
library(DMC21cent)
```


# Subject Level Summary Plots



## Exploring `SEX`

```{r, fig.height=3, fig.width=6}
sl_summary(adsl,
           vars = "SEX",
           kinds = "bar_binom",
           titles = "Female Subjects (%)",
           trt = "TRT01P", 
           base_size = 18)

```


```{r, fig.height=3, fig.width=6}
sl_summary(adsl,
          vars = list("SEX" = "M"),  # `list()` only works for `bar_binom` kind
          kinds = "bar_binom",
          titles = "Male Subjects (%)",
          trt = "TRT01P")
```





```{r, fig.height=4, fig.width=6}
sl_summary(adsl, 
           vars = c(list("SEX" = "M"), "SEX"),
           kinds = c("bar_binom"),
           trt = "TRT01P",
           show_plots = TRUE,
           titles = c("Male Subjects (%)", "Female Subjects (%)"),
           ncol = 1, 
           base_size = 14)

# or you can save the output of sl_summary() in an object.
```


## Exploring `RACE`

```{r, fig.height=3}
sl_summary(adsl,
            vars = "RACE",
            kinds = "bar_stack",        # `bar_stack` visualization will be applied for both `SEX` and `RACE`
            titles = "RACE (%)",  # Put `NA` when you don't need to have a main title for your plot
            trt = "TRT01P")
```



```{r, fig.height=4}
sl_summary(adsl,
            vars = c("RACE", "SEX"),
            kinds = c("bar_stack"),        # `bar_stack` visualization will be applied for both `SEX` and `RACE`
            titles = c("RACE (%)", NA),  # Put `NA` when you don't need to have a main title for your plot
            trt = "TRT01P")
```

## Exploring `AGE`


```{r, fig.height=3, fig.width=6}
sl_summary(adsl,
           vars = "AGEGR1",
           relevel_vec = list(adsl %>% pull(AGEGR1) %>% levels() %>% rev()),
           kinds = "bar_stack",        # `bar_stack` visualization will be applied for both `SEX` and `RACE`
           titles = "AGE Group 1 (%)",  # Put `NA` when you don't need to have a main title for your plot
           trt = "TRT01P")
```


```{r, fig.height=3, fig.width=6}
sl_summary(
  adsl,
  vars = "AGE",
  kinds = "box",
  titles = "Age [years]",
  trt = "TRT01A",
  breaks_vec = list(c(60, 70, 80, 90)),
  show_plots = TRUE,
  base_size = 18
)
```

Show same plot but with th gridlines set to the overall 5-number summary. These are informative gridlines. 

```{r, fig.height=3, fig.width=6}
sl_summary(
  adsl,
  vars = "AGE",
  kinds = "box",
  titles = "Age [years]",
  trt = "TRT01A",
  show_plots = TRUE,
  base_size = 18
)
```


```{r}
plots <- sl_summary(adsl,
            vars = c("SEX", "AGE"),
            kinds = c("bar_stack", "box"),
            titles = c("Female Subjects (%)", "AGE (years)"),
            trt = "TRT01A",
            breaks_vec = list(NULL, c(60, 70, 80, 90)),
            show_plots = FALSE)

patchwork::wrap_plots(plots, ncol = 1)

# In case you want to save your plot:
# ggplot2::ggsave(
#        plots[[1]],
#        filename = here::here("Your_File", "Figure01_sex_f.png"),
#        width = 4,
#        height = 2
#      )

```



# Adverse Event Summary Plots


## Forest Plot

```{r, fig.height=6, fig.width=6}
ae_summary(adae = adae,
            adsl = adsl,
            kind = "forest",
            pval_cutoff = 0.6,
            title = "Adverse events (Preferred Terms), hazard ratios",
            subtitle = "Xanomeline High Dose vs. Placebo, Safety analysis set",
           caption = "Hazard ratio calculated from a Cox regression model."
           )
```


## Rate Plot

```{r, fig.height=8, fig.width=12}
ae_summary(adae = adae,
          adsl = adsl,
          kind = "rate",
          reord_type_rateplot = "diff",
          title = "Adverse events (Preferred Terms), incidence rates",
          subtitle = "Xanomeline High Dose vs. Placebo, Safety analysis set",
          caption = ""
         )
```


```{r}
ae_summary(adae = adae,
          adsl = adsl,
          kind = "rate",
          reord_type_rateplot = "trt",
          title = "Adverse events (Preferred Terms), incidence rates",
          subtitle = "Xanomeline High Dose vs. Placebo, Safety analysis set",
          caption = ""
         )
```


```{r}
ae_summary(adae = adae,
          adsl = adsl,
          kind = "rate",
          reord_type_rateplot = "placebo",
          title = "Adverse events (Preferred Terms), incidence rates",
          subtitle = "Xanomeline High Dose vs. Placebo, Safety analysis set",
          caption = ""
         )
```


## Swimmer Plot


```{r, fig.width = 11, fig.height = 11}
ae_summary(adae = adae,
          adsl = adsl,
          kind = "swimmer",
          title = "Adverse event profiles",
          subtitle = "Patients with at least one treatment-emergent serious or severe AE, Xanomeline High Dose, Safety analysis set",
          caption = "The red and bold fonts show severe and serious events respectively. \n The grey box indicates individual patient Xanomeline exposure."
          )
```


## Volcano Plot



```{r}
ae_summary(adae = adae,
          adsl = adsl,
          kind = "volcano_pval",
          pval_cutoff = 1,
          adjpval_cutoff = 0.9,
          title = "Comparison of adverse events (preferred terms) by treatment",
          subtitle = "Xanomeline High Dose vs. Placebo, Safety analysis set",
          caption = "P-value is from a Cox regression model."
         )
```





```{r}
ae_summary(adae = adae,
          adsl = adsl,
          kind = "volcano_adjpval",
          pval_cutoff = 1,
          adjpval_cutoff = 0.9,
          title = "Comparison of adverse events (preferred terms) by treatment",
          subtitle = "Xanomeline High Dose vs. Placebo, Safety analysis set",
          caption = "P-value is from a Cox regression model, adjusted for multiple comparisons (based on false discovery rate)."
          )
```



# Laboratory Summary Plots

## Abnormal Plot

```{r}
lab_summary(adlb = adlbc,
           kind = "abnormal",
           param_filter = "Cholesterol (mmol/L)",
           selected_visit = c("Baseline", "Week 2", "Week 4", "Week 6", "Week 8", "End of Treatment"),
           title = NULL  # an auto generated title
          )
```

## Box Plot

```{r}
lab_summary(adlb = adlbc,
           kind = "box",
           param_filter = "Cholesterol (mmol/L)",
           selected_visit = c("Baseline", "Week 2", "Week 4", "Week 6", "Week 8", "End of Treatment"),
           title = NULL  # an auto generated title
          )
```

## Shift Plot

```{r}
lab_summary(adlb = adlbhy,
           kind = "shift",
           param_filter = "Alanine Aminotransferase (U/L)",
           title = NULL,  # automatically generated title,
           shift_breaks_vec = NULL # automatically generated 25X breaks, and 50X labels
           )
```


## Spaghetti Plot


```{r}
lab_spaghetti(adlb = adlbc,
              param_filter = "Bilirubin (umol/L)",
              selected_visit = c("Baseline", "Week 2", "Week 4", "Week 6", "Week 8", "End of Treatment"))

```


```{r}
lab_spaghetti(adlb = adlbc,
              param_filter = "Creatine Kinase (U/L)",
              axis_tick_size = 8,
              x_axis_wrap = 6,
              selected_visit = c("Baseline", "Week 2", "Week 4", "Week 6", "Week 8", "End of Treatment"))

```


# Patient Profile

## Summary table

```{r}
patient_profile(data = adsl,
                usubjid = "02-718-1371",
                kind = 'summary')
```



## Laboratory

```{r, out.extra='style="margin-left: 80px;"', fig.width = 9.5, fig.height = 3.5}
patient_profile(data = adlbc,
                usubjid = "02-718-1371",
                kind = 'lab',
                filter_safety_flag_lab = "Y",
                ncol_lab = 1,
                transform_lab = 'log',
                params_lab = c("Alanine Aminotransferase (U/L)",
                                "Aspartate Aminotransferase (U/L)",
                                "Bilirubin (umol/L)"),
                selected_visit = c("Baseline", "Week 2", "Week 4", "Week 6", "Week 8", "End of Treatment"))
```



## Adverse Event

```{r, out.extra='style="margin-left: 180px;"'}
patient_profile(data = adae,
                usubjid = "02-718-1371",
                kind = 'ae',
                str_wrap_ae_cm = 25,
                height_ae = 250)
```


## Concomitant Medications

```{r}
patient_profile(data = adcm,
                usubjid = "02-718-1371",
                str_wrap_ae_cm = 25,
                kind = 'cm')
```


## One Page result


```{r, echo = FALSE}
patient_profile(data = adsl,
                usubjid = "02-718-1371",
                kind = 'summary')

```

```{r, echo = FALSE, out.extra='style="margin-left: 90px;"', fig.width = 10, fig.height = 3.2}

patient_profile(data = adlbc,
                usubjid = "02-718-1371",
                kind = 'lab',
                ncol_lab = 1,
                filter_safety_flag_lab = "Y",
                transform_lab = 'log',
                params_lab = c("Alanine Aminotransferase (U/L)",
                                "Aspartate Aminotransferase (U/L)",
                                "Bilirubin (umol/L)"),
                selected_visit = c("Baseline", "Week 2", "Week 4", "Week 6", "Week 8", "End of Treatment"))

```

```{r, echo = FALSE, fig.width = 8.9, fig.height = 8.8}

patient_profile(data = adae,
                usubjid = "02-718-1371",
                kind = 'ae',
                str_wrap_ae_cm = 25,
                height_ae = 250)

```

```{r, echo = FALSE, fig.width = 8.8, fig.height = 8.8}

patient_profile(data = adcm,
                usubjid = "02-718-1371",
                str_wrap_ae_cm = 25,
                kind = 'cm')
```


